Laplacian envelope

### 2020-10-17 Notes/laplace.tex
notes on sqrt bound

% -*- TeX -*- -*- UK -*-
% ----------------------------------------------------------------
% arXiv Paper ************************************************
%
% Subhaneil Lahiri's template
%
% Before submitting:
%    Comment out hyperref
%    Comment out showkeys
%    Replace \input{?.tex} with its contents
%       or include ?.tex in zip/tar file
%    Put this file, the .bbl file, any picture or
%       other additional files and natbib.sty
%       file in a zip/tar file
%
% **** -----------------------------------------------------------
\documentclass[12pt]{article}
%Preamble:
\usepackage{a4wide}
\input{sl_preamble.tex}
\usepackage{mathtools}
%
% >> Only for drafts! <<
\usepackage[notref,notcite]{showkeys}
%
\input{sl_graphics_preamble.tex}
\graphicspath{{Figures/}}
%
% ----------------------------------------------------------------
%\numberwithin{equation}{section}
%\renewcommand{\baselinestretch}{1.5}
% ----------------------------------------------------------------
% New commands etc.
\input{sl_definitions.tex}
\input{sl_symbols.tex}
%matrices
%vec of ones
\newcommand{\onev}{\mathbf{e}}
%mat of ones
\newcommand{\onem}{\mathbf{E}}
%Markov matrix
\newcommand{\MM}{\mathbf{Q}}
%prob distribution
\newcommand{\pr}{\mathbf{p}}
%equilibrium distribution
\newcommand{\eq}{\pib}
%equilibrium metric
\newcommand{\Eq}{\boldsymbol{\Pi}}
%first passage times
\newcommand{\fpt}{\mathbf{T}}
%off-diag first passage times
\newcommand{\fptb}{\overline{\fpt}}
%fundamental matrix
\newcommand{\fund}{\mathbf{Z}}
%other symbols
\newcommand{\Pb}{\mathbf{P}}
\newcommand{\D}{\mathbf{D}}
\newcommand{\pib}{\boldsymbol{\pi}}
\newcommand{\arow}{\boldsymbol{\xi}}
\newcommand{\Lb}{\boldsymbol{\Lambda}}
\newcommand{\lb}{\boldsymbol{\lambda}}
\newcommand{\etw}{\boldsymbol{\eta}^w}
\newcommand{\thb}{\boldsymbol{\theta}}
\newcommand{\omb}{\boldsymbol{\omega}}
\newcommand{\alb}{\boldsymbol{\alpha}}
%synapse models
\newcommand{\w}{\mathbf{w}}
\newcommand{\W}{\mathbf{W}}
\newcommand{\M}{\mathbf{M}}
\newcommand{\enc}{\mathbf{K}}
\newcommand{\frg}{\W^{\mathrm{F}}}
\newcommand{\F}{\boldsymbol{\Phi}}
%superscripts
\newcommand{\pot}{^{\text{pot}}}
\newcommand{\dep}{^{\text{dep}}}
\newcommand{\potdep}{^{\text{pot/dep}}}
%with activity indep processes
\renewcommand{\hom}{\mathbf{H}}
\newcommand{\Mh}{\widetilde{\M}}
\newcommand{\frgh}{\widetilde{\W}^{\mathrm{F}}}
\newcommand{\ench}{\widetilde{\enc}}
%eigenvectors
\newcommand{\evr}{\mathbf{u}}
\newcommand{\evl}{\boldsymbol{\eta}}
%snr curves etc
\newcommand{\syn}{\vec{w}}
\newcommand{\synid}{\syn_\text{id}}
\DeclareMathOperator{\SNR}{SNR}
\DeclareMathOperator{\snr}{SNR}
\DeclareMathOperator{\NNR}{NNR}
\DeclareMathOperator{\nnr}{NNR}
\newcommand{\snrb}{\overline{\snr}}
\DeclareMathOperator{\env}{Env}
\newcommand{\rh}{\hat{r}}
\newcommand{\CA}{\mathcal{A}}
\newcommand{\CB}{\mathcal{B}}
%avoid double superscripts
\renewcommand{\pdiff}[2]{\frac{\partial #1}{\partial #2}}
% shifted process
\newcommand{\shift}[1]{\widehat{#1}}

@@

@@

Given a sequence of plasticity events at times $t_1,t_2,t_3,\ldots$, the probability distribution across the internal states at time $t_n$, 
mariginalising over states at earlier times, is
%
\begin{equation}\label{eq:plastseq}
  \pr(t_n) = \pr(t_0)  \M\pot \M\dep \M\dep \M\pot \M\dep \M\pot \M\pot \M\dep \ldots \M\pot .
\end{equation}
%
If the probability of a given plasticity event being potentiating/depressing is $f\potdep$, the probability of the sequence above (conditioned on the number of events) is given by $f\pot f\dep f\dep f\pot f\dep f\pot f\pot f\dep \ldots f\pot$.

In computing the expectation in \eqref{eq:overlapone} the plasticity event that occurs at $t=0$ is fixed, but all of the previous and subsequent events are marginalised over.
If we marginalise over the types (potentiating/depressing) of these other events (conditioned on the number of events) we find
%
\begin{multline}\label{eq:plastseqtypes}
  \pr(t_n) = \pr(t_0) (f\pot\M\pot+f\dep\M\dep)  \ldots (f\pot\M\pot+f\dep\M\dep) \\
    \M\potdep (f\pot\M\pot+f\dep\M\dep) \ldots (f\pot\M\pot+f\dep\M\dep),
\end{multline}
%
where the factor of $\M\potdep$ is the event at $t=0$.
If we expand out all of the parenthetical factors, we will get a sum of terms of the form \eqref{eq:plastseq} weighted by their probabilities.

@@

@@

We can also express this in terms of the shifted process in \cref{eq:larea}.
We can choose how to distribute the shift across \(\M\pot\) and \(\M\dep\).
Two choices from a continuum%
\footnote{We could choose \( \shift{\M}^\nu(s) = \M^\nu + \frac{s g^\nu}{r f^\nu} (\onev \eq - \I) \), for any \(g^\nu \) with \( \sum_\nu g^\nu = 1 \).
The two possibilities in \cref{eq:lshiftpd} come from \(g^\nu = \frac{1}{2}\) and \(g^\nu = f^\nu\) respectively.}
are:
%
\begin{equation}\label{eq:lshiftpd}
  \shift{\M}^\nu(s) = \M^\nu + \frac{s}{2 r f^\nu} (\onev \eq - \I)
  \qquad \text{or} \qquad
  \shift{\M}^\nu(s) = \M^\nu + \frac{s}{r} (\onev \eq - \I).
\end{equation}
%
The first choice leaves \( \shift{\enc} = \enc \), so it only affects the \(\etw\) piece of \cref{eq:larea}.
The second choice does not leave \(\enc\) invariant (in fact \( \shift{\enc}(s) = \enc + (f\pot - d\dep) (\onev \eq - \I) \)), but because \( \eq (\onev \eq - \I) = 0 \) the shift does not make any contribution to \cref{eq:larea}.
Either way:
%
\begin{equation}\label{eq:lareashift}
  \hat{A}\prn{s; \M^\nu} = \hat{A}\prn{0; \shift{\M}^\nu(s)}.
\end{equation}
%
In other words, the laplace transform of the SNR is the area under the SNR for the shifted process.

@@

@@

@@

Now we introduce an eigenvector decomposition for $-\frg$:
%
\begin{equation}\label{eq:eigendecomp}
  \frg = - \sum_a q_a \evr^a \evl^a,
  \quad
  \evl^a \evr^b = \delta_{ab},
  \quad
  \frg \evr^a = -q_a \evr^a,
  \quad
  \evl^a \frg = -q_a \evl^a.
\end{equation}
%
Then we can write
%
\begin{equation}\label{eqsnreig}
  \snr(t) = \sqrt{N}\sum_a \CI_a \e^{-rt/\tau_a},
  \qquad
  \snrb(\tau) = \sqrt{N}\sum_a \frac{\CI_a}{1+r\tau/\tau_a},
\end{equation}
%
where
%
\begin{equation}\label{eq:snrcoeffs}
  \CI_a = (\eq \ench \evr^a) (\evl^a \w),
  \qquad
  \tau_a = \frac{1}{q_a}.
\end{equation}
%
From \eqref{eq:areabnd} and \eqref{eq:initbnd}, we see that they are subject to the constraints
%
\begin{equation}\label{eq:coeffconstr}
  \sum_a \CI_a \tau_a \leq M-1,
  \qquad
  \sum_a \CI_a \leq 1.
\end{equation}
%
No doubt there are many other constraints that these quantities must satisfy, but we can see what these ones imply for the $\snrb(\tau)$ by maximising it subject to these constraints.

>>>>

% -*- TeX -*- -*- UK -*-
% ----------------------------------------------------------------
% arXiv Paper ************************************************
%
% Subhaneil Lahiri's template
%
% Before submitting:
%    Comment out hyperref
%    Comment out showkeys
%    Replace \input{?.tex} with its contents
%       or include ?.tex in zip/tar file
%    Put this file, the .bbl file, any picture or
%       other additional files and natbib.sty
%       file in a zip/tar file
%
% **** -----------------------------------------------------------
\documentclass[12pt]{article}
%Preamble:
\usepackage[T1]{fontenc}
\usepackage{a4wide}
\usepackage{stix}
% Preamble:
%\usepackage{a4wide}
%\usepackage{ams} for finding documentation only
\usepackage[centertags]{amsmath}
% \usepackage{amssymb}
\usepackage{xcolor}
\usepackage[sort&compress,numbers]{natbib}
\usepackage{ifpdf}
%
\ifpdf
 \usepackage[pdftex,bookmarks,bookmarksopen,pdfstartview=FitH,bookmarksnumbered]{hyperref}
\else
 \usepackage[hypertex]{hyperref}
\fi
% ----------------------------------------------------------------
\vfuzz2pt % Don't report over-full v-boxes if over-edge is small
\hfuzz2pt % Don't report over-full h-boxes if over-edge is small
% ----------------------------------------------------------------
\def\Snospace~{\S{}}
\renewcommand{\sectionautorefname}{\Snospace}
\renewcommand{\subsectionautorefname}{\Snospace}
\renewcommand{\subsubsectionautorefname}{\Snospace}
\usepackage{cleveref}
\usepackage{mathtools}
%
% >> Only for drafts! <<
\usepackage[notref,notcite]{showkeys}
%
\input{sl_graphics_preamble.tex}
\graphicspath{{Figures/}}
%
% ----------------------------------------------------------------
%\numberwithin{equation}{section}
%\renewcommand{\baselinestretch}{1.5}
% ----------------------------------------------------------------
% New commands etc.
\input{sl_definitions.tex}
\input{sl_symbols.tex}
%matrices
%vec of ones
\newcommand{\onev}{\mathbf{e}}
%mat of ones
\newcommand{\onem}{\mathbf{E}}
%Markov matrix
\newcommand{\MM}{\mathbf{Q}}
%prob distribution
\newcommand{\pr}{\mathbf{p}}
%equilibrium distribution
\newcommand{\eq}{\pib}
%equilibrium metric
\newcommand{\Eq}{\boldsymbol{\Pi}}
%first passage times
\newcommand{\fpt}{\mathbf{T}}
%off-diag first passage times
\newcommand{\fptb}{\overline{\fpt}}
%fundamental matrix
\newcommand{\fund}{\mathbf{Z}}
%other symbols
\newcommand{\Pb}{\mathbf{P}}
\newcommand{\D}{\mathbf{D}}
\newcommand{\pib}{\boldsymbol{\pi}}
\newcommand{\arow}{\boldsymbol{\xi}}
\newcommand{\Lb}{\boldsymbol{\Lambda}}
\newcommand{\lb}{\boldsymbol{\lambda}}
\newcommand{\etw}{\boldsymbol{\eta}^w}
\newcommand{\thb}{\boldsymbol{\theta}}
\newcommand{\omb}{\boldsymbol{\omega}}
\newcommand{\alb}{\boldsymbol{\alpha}}
%synapse models
\newcommand{\w}{\mathbf{w}}
\newcommand{\W}{\mathbf{W}}
\newcommand{\M}{\mathbf{M}}
\newcommand{\enc}{\mathbf{K}}
\newcommand{\frg}{\W^{\mathrm{F}}}
\newcommand{\F}{\boldsymbol{\Phi}}
%superscripts
\newcommand{\pot}{^{\text{pot}}}
\newcommand{\dep}{^{\text{dep}}}
\newcommand{\potdep}{^{\text{pot/dep}}}
%with activity indep processes
\renewcommand{\hom}{\mathbf{H}}
\newcommand{\Mh}{\widetilde{\M}}
\newcommand{\frgh}{\widetilde{\W}^{\mathrm{F}}}
\newcommand{\ench}{\widetilde{\enc}}
%eigenvectors
\newcommand{\evr}{\mathbf{u}}
\newcommand{\evl}{\boldsymbol{\eta}}
%snr curves etc
\newcommand{\syn}{\vec{w}}
\newcommand{\synid}{\syn_\text{id}}
\DeclareMathOperator{\SNR}{SNR}
\DeclareMathOperator{\snr}{SNR}
\DeclareMathOperator{\NNR}{NNR}
\DeclareMathOperator{\nnr}{NNR}
\newcommand{\snrb}{\overline{\snr}}
\DeclareMathOperator{\env}{Env}
\newcommand{\rh}{\hat{r}}
\newcommand{\CA}{\mathcal{A}}
\newcommand{\CB}{\mathcal{B}}
%avoid double superscripts
\renewcommand{\pdiff}[2]{\frac{\partial #1}{\partial #2}}
% shifted process
\newcommand{\shift}[1]{\widehat{#1}}

@@

%--------------------------------------------------------------------------------

@@

Given a sequence of plasticity events at times $t_1,t_2,t_3,\ldots$, the probability distribution across the internal states at time $t_n$, 
mariginalising over states at earlier times, is
%
\begin{equation}\label{eq:plastseq}
  \pr(t_n) = \pr(t_0)  \M\pot \M\dep \M\dep \M\pot \M\dep \M\pot \M\pot \M\dep \ldots \M\pot .
\end{equation}
%
If the probability of a given plasticity event being potentiating or depressing is $f\pot$ or $f\dep$ respectively, the probability of the sequence above (conditioned on the number of events) is given by $f\pot f\dep f\dep f\pot f\dep f\pot f\pot f\dep \ldots f\pot$.

In computing the expectation in \eqref{eq:overlapone} the plasticity event that occurs at $t=0$ is fixed, but all of the previous and subsequent events are marginalised over.
If we marginalise over the types (potentiating/depressing) of these other events (conditioned on the number of events) we find
%
\begin{multline}\label{eq:plastseqtypes}
  \pr(t_n) = \pr(t_0) (f\pot\M\pot+f\dep\M\dep)  \ldots \\
    \ldots (f\pot\M\pot+f\dep\M\dep) 
    \M\potdep (f\pot\M\pot+f\dep\M\dep) \ldots \\
    \ldots (f\pot\M\pot+f\dep\M\dep),
\end{multline}
% 
where the factor of $\M\potdep$ is the event at $t=0$.
If we expand out all of the parenthetical factors, we will get a sum of terms of the form \eqref{eq:plastseq} weighted by their probabilities.

@@

%================================================================================

@@

We can also express this in terms of the shifted process in \cref{eq:larea}.
We can choose how to distribute the shift across \(\M\pot\) and \(\M\dep\).
Two choices from a continuum%
\footnote{We could choose \( \shift{\M}^\nu(s) = \M^\nu + \frac{s g^\nu}{r f^\nu} (\onev \eq - \I) \), for any \(g^\nu \) with \( \sum_\nu g^\nu = 1 \).
The two possibilities in \cref{eq:lshiftpd} come from \(g^\nu = \frac{1}{2}\) and \(g^\nu = f^\nu\) respectively.}
are:
%
\begin{equation}\label{eq:lshiftpd}
  \shift{\M}^\nu(s) = \M^\nu + \frac{s}{2 r f^\nu} (\onev \eq - \I)
  \qquad \text{or} \qquad
  \shift{\M}^\nu(s) = \M^\nu + \frac{s}{r} (\onev \eq - \I).
\end{equation}
%
The first choice leaves \( \shift{\enc} = \enc \), so it only affects the \(\etw\) piece of \cref{eq:larea}.
The second choice does not leave \(\enc\) invariant (in fact \( \shift{\enc}(s) = \enc + (f\pot - f\dep) (\onev \eq - \I) \)), but because \( \eq (\onev \eq - \I) = 0 \) the shift does not make any contribution to \cref{eq:larea}.
Either way:
%
\begin{equation}\label{eq:lareashift}
  \hat{A}\prn{s; \M^\nu} = \hat{A}\prn{0; \shift{\M}^\nu(s)}.
\end{equation}
%
In other words, the laplace transform of the SNR is the area under the SNR for the shifted process.

@@

Now to study the SNR as a function of  time, it helps to consider some variables that are more directly related to the time dependance than the matrix elements. 
So we introduce an eigenvector decomposition for $-\frg$:
%
\begin{equation}\label{eq:eigendecomp}
  \frg = - \sum_a q_a \evr^a \evl^a,
  \quad
  \evl^a \evr^b = \delta_{ab},
  \quad
  \frg \evr^a = -q_a \evr^a,
  \quad
  \evl^a \frg = -q_a \evl^a.
\end{equation}
%
Then we can write
%
\begin{equation}\label{eq:snreig}
  \snr(t) = \sqrt{N}\sum_a \CI_a \e^{-rt/\tau_a},
  \qquad
  \snrb(\tau) = \sqrt{N}\sum_a \frac{\CI_a}{1+r\tau/\tau_a},
\end{equation}
%
where
%
\begin{equation}\label{eq:snrcoeffs}
  \CI_a = (\eq \enc \evr^a) (\evl^a \w),
  \qquad
  \tau_a = \frac{1}{q_a}.
\end{equation}
%
Now the question is what are the allowed values of \( (\CI_a, \tau_a) \)?
We have to translate the constraints of \cref{eq:constri} into constraints on the eigenmode variables.
Each constraint we find will be a necessary condition for the existence of a set of Markov processes \( \M_{ij}^\nu \) that result in \( (\CI_a, \tau_a) \).
We can imagine the notion of a complete set of constraints: constraints that, when combined, are also sufficient for the existence of a \( \M_{ij}^\nu \).
But finding such a set seems intractable for now.
Most likely there are a large number of such constraints, but if we can find a few of them they will provide us with some limits on the space of possible memory curves.
These limits may not be tight - there may not be models that can reach these limits, but they will imply a forbidden region in the space of memory curves.

%--------------------------------------------------------------------------------

@@

\subsection{Square-root bound}\label{sec:sqrt}

\newcommand{\aav}[1]{\mathopen{}\left\lAngle #1 \right\rAngle\mathclose{}}
\newcommand{\nnrm}[1]{\mathopen{}\left\Vvert #1 \right\Vvert\mathclose{}}

This proof follows that of \cite{Lawler1988cheeger}.
We can define two inner-products that will be of use.
The first is the usual inner product of two vectors (or functions on state space in the continuum case) using the steady state distribution as the measure:
%
\begin{equation}\label{eq:innereq}
  \av{\mathbf{u}, \mathbf{v}} = \sum_i \eq_i u_i^\ast v_i ,
  \qquad
  \nrm{\mathbf{v}} = \sqrt{\av{\mathbf{v}, \mathbf{v}}} .
\end{equation}
%
The second is an inner product of rank 2 tensors (functions of pairs of points on state space) using the steady-state flux as the measure:
%
\begin{equation}\label{eq:innerflux}
  \aav{\mathbf{F}, \mathbf{G}} = \sum_{i \neq j} \F_{ij} F_{ij}^\ast G_{ij} ,
  \qquad
  \nnrm{\mathbf{F}} = \sqrt{\aav{\mathbf{F}, \mathbf{F}}}.
\end{equation}
%
The omission of the diagonal terms leaves only non-negative terms.

When the process satisfies detailed balance, \ie \(\F_{ij}\) is symmetric, we can relate these inner products to quantities of interest.

We can write
%
\begin{equation*}
  \av{\mathbf{u}, -\MM\mathbf{v}} = \sum_{i \neq j} \eq_i u_i^\ast \MM_{ij} (v_i - v_j),
\end{equation*}
%
under detailed balance, we can symmetrize
%
\begin{equation*}
  \av{\mathbf{u}, -\MM \mathbf{v}} 
      = \frac{1}{2}\sum_{i \neq j} \F_{ij} (u_i^\ast - u_j^\ast) (v_i - v_j) 
      = \frac{1}{2} \aav{\boldsymbol{\Delta}\mathbf{u}, \boldsymbol{\Delta}\mathbf{v}}.
\end{equation*}
%

The eigenvalue spectrum of \(\MM\) is closely related to its numerical range:
%
\begin{equation}\label{eq:numrange}
  \mathcal{W}(-\MM; \mathcal{V}) 
    = \set{\frac{\av{\mathbf{u}, -\MM \mathbf{u}}}{\av{\mathbf{u}, \mathbf{u}}}}
          {\mathbf{u} \in \mathcal{V}} 
    = \set{\frac{\nnrm{\boldsymbol{\Delta}\mathbf{u}}^2}{2\nrm{\mathbf{u}}^2}}
          {\mathbf{u} \in \mathcal{V}} .
\end{equation}
%
When \(\MM\) satisfies detailed balance (more generally when it commutes with its time reverse), the numerical range is the convex hull of the eigenvalues.

The other quantity of interest in \cref{eq:snrcoeffs} is the amplitude of the eigenmodes.
In analogy, we define the following functional (for real \(\mathbf{u}\))
%
\begin{equation*}
  \CI(\mathbf{u}) = \frac{(\eq \enc \mathbf{u}) (\mathbf{u}^\dag \w)}{\mathbf{u}^\dag \mathbf{u}}
      = \frac{\sum_{i \neq j} \eq_i \enc_{ij} (u_j - u_i) \sum_k \eq_k u_k \w_k} 
             {\sum_{l} \eq_l u_l^2} .
\end{equation*}
%
Following \cite{Lawler1988cheeger}, we can write
%
\begin{equation*}
  u_j - u_i = \intd[_{u_i}^{u_j}]{\alpha} 
      = \intd[_{-\infty}^{\infty}]{\alpha} 
        \brk{\vartheta(u_j - \alpha) \vartheta(\alpha - u_i) 
           - \vartheta(u_i - \alpha) \vartheta(\alpha - u_j)} ,
\end{equation*}
%
where \(\vartheta\) is the Heaviside step-function.
Then 
%
\begin{equation*}
  \begin{aligned}[t]
  r \eq \enc \mathbf{u} &= \intd[_{-\infty}^{\infty}]{\alpha}  \brk{
        \F\pot_{\CA_\alpha \CA_\alpha^c} - \F\dep_{\CA_\alpha \CA_\alpha^c} 
      - \F\pot_{\CA_\alpha^c \CA_\alpha} + \F\dep_{\CA_\alpha^c \CA_\alpha} }
    \\
    &= \intd[_{-\infty}^{\infty}]{\alpha}  \brk{
        \F_{\CA_\alpha \CA_\alpha^c} + \F_{\CA_\alpha^c \CA_\alpha} 
        - 2\F\dep_{\CA_\alpha \CA_\alpha^c} - 2\F\pot_{\CA_\alpha^c \CA_\alpha} }
  \end{aligned}
  %
  \quad \text{where} \quad
  %
  \begin{aligned}[t]
    \CA_\alpha &= \set{i}{u_i < \alpha} 
    , \\
    \F^\nu_{\CA \CB} &= r f^\nu \sum_{\substack{i \in \CA \\ j \in \CB}} 
                        \prn{\M^\nu_{ij} - \delta_{ij}}
    .
  \end{aligned}
\end{equation*}
%
In exactly the same way as the proof of \cref{eq:initbnd}, we can argue that the two terms with the negative signs are indeed non-positive as they do not involve the negative diagonal elements of~\( \F_{ij}^\nu \).
Therefore the other terms provide an upper bound.
%
\begin{equation*}
\begin{aligned}
  r \nrm{\mathbf{u}}^2 \CI(\mathbf{u}) 
      &\leq \intd[_{-\infty}^{\infty}]{\alpha}  \brk{
        \F_{\CA_\alpha \CA_\alpha^c} + \F_{\CA_\alpha^c \CA_\alpha} } 
        \av{\mathbf{u}, \w}
  \\  &= \intd[_{-\infty}^{\infty}]{\alpha} \sum_{i \neq j} \F_{ij} \brk{
            \vartheta(u_j - \alpha) \vartheta(\alpha - u_i) 
          + \vartheta(u_i - \alpha) \vartheta(\alpha - u_j)
        } \av{\mathbf{u}, \w}
  \\  &= \sum_{i \neq j} \F_{ij} \abs{u_j - u_i} \av{\mathbf{u}, \w}
  \\  &= \aav{\abs{\boldsymbol{\Delta}\mathbf{u}}, \onem} \av{\mathbf{u}, \w} .
\end{aligned}
\end{equation*}
%
Now we can apply the Cauchy-Schwartz inequality to both factors to find
%
\begin{equation*}
  r \CI(\mathbf{u}) \leq \nnrm{\boldsymbol{\Delta}\mathbf{u}} \nnrm{\onem} 
                          \nrm{\mathbf{u}} \nrm{\w}.
\end{equation*}
%
We also have \( \nrm{\w}^2 = \sum_i \eq_i \w_i^2 = 1 \).
Furthermore, using \cref{eq:constri}, \( \nnrm{\onem}^2 = \sum_{i \neq j} \eq_i \MM_{ij} \leq r \sum_i \eq_i = r\).
Then, remembering \cref{eq:numrange},
%
\begin{equation}\label{eq:sqrtnumrange}
  \sqrt{r} \CI(\mathbf{u}) \leq \sqrt{2\mathcal{W}(-\MM, \mathbf{u})}.
\end{equation}
%
Now, simply choosing \(\mathbf{u} = \evr_a \), one of the orthonormal eigenvectors, we find a bound on the eigenmodes:
%
\begin{equation}\label{eq:sqrtbound}
  \text{assuming} \quad 
  \eq_i \MM_{ij} = \eq_j \MM_{ji},
  \qquad \text{we have} \quad
  \CI_a \sqrt{\tau_a} \leq \sqrt{2}.
\end{equation}
%

%--------------------------------------------------------------------------------

@@

Recall the eigenmode description of the memory curve from \cref{eq:snreig}
%
\begin{equation*}
  \snr(t) = \sqrt{N}\sum_a \CI_a \e^{-rt/\tau_a},
  \qquad
  \snrb(\tau) = \sqrt{N}\sum_a \frac{\CI_a}{1+r\tau/\tau_a},
\end{equation*}
%
where
%
\begin{equation*}
  \CI_a = (\eq \ench \evr^a) (\evl^a \w),
  \qquad
  \tau_a = \frac{1}{q_a}.
\end{equation*}
%
From \eqref{eq:areabnd} and \eqref{eq:initbnd}, we see that they are subject to the constraints
%
\begin{equation}\label{eq:coeffconstr}
  \sum_a \CI_a \tau_a \leq M-1,
  \qquad
  \sum_a \CI_a \leq 1.
\end{equation}
%
No doubt there are many other constraints that these quantities must satisfy, but we can see what these ones imply for the $\snrb(\tau)$ by maximising it subject to these constraints.
